Comparison of approaches to using machine learning models to increase the efficiency of the global search algorithm for solving multicriterial problems

### 2024-06-28 2024/OPTIMA/OPTIMA_2024_MCO.tex
check current part

Each iteration of the search consists of one trial execution. The term ``trial'' means evaluation of the minimized function $\varphi(x)$ from (\ref{eq:07}) at some point.

@@

Let $k$, $k \geq 2$, search iterations have been executed at trial points $x^0, x^1,\dots,x^{k-1}$ with objective function values, where $z^0, z^1,\dots,z^{k-1}$, $z^i=\varphi(x^i)$, $1 \leq i \leq k-1$. Then the choice of the new trial point $x^k$ is determined according to the following rules.

\textit{Rule 1.} Renumber by subscripts all trial points in increasing order
\begin{equation}
    \label{eq:09}
    x_0 = 0 < x_1 < \dots < x_i < \dots < x_{k} = 1.
\end{equation}
and juxtapose to them the values $z_i=\varphi(x_i)$, $1 \leq i \leq k-1$.

@@

\begin{equation}
    \label{eq:10}
		\begin{matrix}
		m=\begin{cases}
				\begin{matrix}
					 r M, & M >0 \\
					 1, & M = 0 
				\end{matrix} 
			\end{cases} ,
		M = \max_{1 \leq i \leq k-1} \frac{| z_i - z_{i-1}|}{\varrho_i}, \\
		z_i = \varphi( x_i ), \varrho_i=\sqrt[N]{x_i-x_{i-1}}
		\end{matrix}
\end{equation}
where $r$, $r>1$ is the \textit{reliability} parameter of the algorithm.

>>>>

Each iteration of the search consists of one trial execution. The term ``trial'' means evaluation of the objective function $\varphi(y(x))$ from (\ref{eq:07}) at some point.

@@

Let $k$, $k \geq 2$, search trials have been executed at the points $x^0, x^1,\dots,x^{k-1}$ with the objective function values $z^i=\varphi(y(x^i))$, $1 \leq i \leq k-1$. Then the choice of the new trial point $x^k$ is determined according to the following rules.

\textit{Rule 1.} Renumber by subscripts all trial points in increasing order
\begin{equation}
    \label{eq:09}
    0 = x_0 < x_1 < \dots < x_i < \dots < x_{k-1} = 1.
\end{equation}
and juxtapose to them the values $z_i=\varphi(y(x_i))$, $1 \leq i \leq k-1$.

@@

\begin{equation}
    \label{eq:10}
		\begin{matrix}
		m=\begin{cases}
				\begin{matrix}
					 r M, & M >0 \\
					 1, & M = 0 
				\end{matrix} \; , 
			\end{cases}
		M = \max_{1 \leq i \leq k-1} \frac{| z_i - z_{i-1}|}{\varrho_i}, \\
		z_i = \varphi( y(x_i) ), \varrho_i=\sqrt[N]{x_i-x_{i-1}}
		\end{matrix}
\end{equation}
where $r>1$ is the \textit{reliability} parameter of the algorithm.
